\textbf{Solution:}

\begin{itemize}

\item \textbf{Memory Access Instructions:} 

In MIPS, \textbf{memory access} instructions are typically the following\footfullcite{MIPS32}:
\begin{itemize}
    \item \texttt{lw} (load word): Loads a value from memory into a register.
    \item \texttt{sw} (store word): Stores a value from a register into memory.
    \item \sout{\texttt{andi} (AND immediate): Used for bitwise operations but does not access memory.}
    \item \sout{\texttt{sll} (shift left logical): Used for shifting bits but does not access memory.}
    \item \sout{\texttt{sra} (shift right arithmetic): Used for shifting bits but does not access memory.}
    \item \sout{\texttt{lui} (load upper immediate): Load the upper part of an address but does not access memory.}
\end{itemize}

\item \textbf{Memory Access Instructions in O0:}

\begin{enumerate}
    \tiny
    \item \texttt{sw \$fp, 4(\$sp)} (line 7) \\
    \textbf{Memory access}: Stores the value of \texttt{\$fp} into memory.

    \item \texttt{lw \$2, \%lo(m\_z)(\$2)} (line 10) \\
    \textbf{Memory access}: Loads the value from memory into register \texttt{\$2}.

    \item \texttt{lw \$2, \%lo(m\_z)(\$2)} (line 26) \\
    \textbf{Memory access}: Loads the value from memory into register \texttt{\$2}.

    \item \texttt{sw \$3, \%lo(m\_z)(\$2)} (line 31) \\
    \textbf{Memory access}: Stores the value from register \texttt{\$3} into memory.

    \item \texttt{lw \$2, \%lo(m\_w)(\$2)} (line 33) \\
    \textbf{Memory access}: Loads the value from memory into register \texttt{\$2}.

    \item \texttt{lw \$2, \%lo(m\_w)(\$2)} (line 44) \\
    \textbf{Memory access}: Loads the value from memory into register \texttt{\$2}.

    \item \texttt{sw \$3, \%lo(m\_w)(\$2)} (line 49) \\
    \textbf{Memory access}: Stores the value from register \texttt{\$3} into memory.

    \item \texttt{lw \$2, \%lo(m\_z)(\$2)} (line 51) \\
    \textbf{Memory access}: Loads the value from memory into register \texttt{\$2}.

    \item \texttt{lw \$2, \%lo(m\_w)(\$2)} (line 55) \\
    \textbf{Memory access}: Loads the value from memory into register \texttt{\$2}.

    \item \texttt{lw \$fp, 4(\$sp)} (line 59) \\
    \textbf{Memory access}: Loads the value from memory into register \texttt{\$fp}.
\end{enumerate}

\begin{itemize}
    \item \texttt{lw} (load word) instructions: 7 instances.
    \item \texttt{sw} (store word) instructions: 3 instances.
    \item In total: $7 + 3 = \boxed{10}$
\end{itemize}

\item \textbf{Memory Access Instructions in the O3:}

\begin{enumerate}
    \tiny
    \item \texttt{lw \$7, \%lo(m\_z)(\$9)} (line 3) \\
    \textbf{Memory access}: Loads the value from memory into register \texttt{\$7}.

    \item \texttt{lw \$6, \%lo(m\_w)(\$8)} (line 8) \\
    \textbf{Memory access}: Loads the value from memory into register \texttt{\$6}.

    \item \texttt{sw \$2, \%lo(m\_w)(\$8)} (line 30) \\
    \textbf{Memory access}: Stores the value from register \texttt{\$2} into memory.

    \item \texttt{sw \$3, \%lo(m\_z)(\$9)} (line 31) \\
    \textbf{Memory access}: Stores the value from register \texttt{\$3} into memory.
\end{enumerate}

\begin{itemize}
    \item \texttt{lw} (load word) instructions: 2 instances.
    \item \texttt{sw} (store word) instructions: 2 instances.
    \item In total: $2 + 2 = \boxed{4}$
\end{itemize}

\end{itemize}